### 2015-07-06 narrative/qos.tex
done for now and will come back to it.

\paragraph{Resource Management Background:} There is an important connection between finding the resources
that can help fulfill a particular request and the performance predictability of that request, which demands
careful resource management strategies. This connection is particularly important for reading - in very large 
scale systems, finding a resource to read can be a significant, if not dominant, component of overall read 
latency.

Locating resources is a typical distributed systems problem. Centralized solutions are limited in their
scalability, because typically there exists a single entity that tracks every update in the system. 
Traditional file systems are good examples 
for this: most updates to files require updates to their centrally maintained block allocation tables. 
The opposite of file systems are ``pile'' systems, which, instead of keeping track of updates, search for 
resources at request time. Pile systems allow very efficient writes because clients can write whereever
there is free space and there is very low bookkeeping overhead. Furthermore, pile systems have great
flexibility for moving resources around, for example to ensure durability. However, reads require a 
potentially unbounded search, especially if it is not clear whether the resource actually exists. 
Methods to make searches more efficient without reverting to centralized bookkeeping usually involves 
some kind of partitioning of the search space and a method to limit the search to a small number of partitions.

>>>>

\paragraph{Resource Management Background:} There is an important connection between finding the resources
that can help fulfill a particular request and the performance predictability of that request, and this demands
careful resource management strategies that deal with large number of data chunks spread across storage hierarchy. 
%This connection is particularly important for data retrieval 
%- in large scale storage systems, finding a resource to read can be a significant, if not dominant, 
%component of overall read latency. 
Locating resources is a typical distributed systems problem. Centralized solutions are limited in their
scalability, because there exists a single entity that tracks updates in the system. 
Traditional file systems are good examples for this: most updates to files require updates 
to their centrally maintained block allocation tables. 
The opposite of file systems are ``pile'' systems, which, instead of keeping track of updates, search for 
resources at request time. Pile systems allow very efficient writes because clients can write whereever
there is free space and there is very low bookkeeping overhead. However, unbounded search is possible, 
if it is unclear whether the resource actually exists. 
Methods to make searches more efficient without reverting to centralized bookkeeping usually involves 
some kind of partitioning of the search space and a method to limit the search to a small number of partitions.
